Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-07 p2/def-filesystem.tex
Single directory value assumption

To avoid the proliferation of edge cases, we will furthermore suppose that
$|\setd|=1$, that is, there is only one directory value $\vald\in\setv$, and so
apart from their location, all directories are equal.
In appendix TODO we describe why it can be a sensible choice
for actual synchronizers, and we also present an encoding that makes it possible
to extend our results to the $|\setd|>1$ case.

@@

\myskip
In the rest of this paper,
we fix the skeleton $\langle\setn,\parent\rangle$,
and the set of values $\setv$.
$\FS$ (with or without indices) denotes a filesystem,
and $n$, $m$ and $o$ are nodes in $\setn$.

>>>>

An essential assumption in our model is that there is only
a \emph{single directory value} ($|\setd|=1$).
The realisation that
this creates a symmetry between directories and empty nodes
that allows formulating a correct and complete reconciliation algorithm
is one of the main contributions of this paper.
This assumption does not hinder the applicability of our results
(in fact, many real-life synchronizers make the same assumption),
but makes it possible to exploit a hidden symmetry in filesystem commands.

% TODO To avoid the proliferation of edge cases
% TODO In appendix TODO we describe why it can be a sensible choice
% TODO for actual synchronizers, and we also present an encoding that makes it possible
% TODO to extend our results to the $|\setd|>1$ case.

@@

\myskip
In this paper
we fix the skeleton $\langle\setn,\parent\rangle$,
and the set of values $\setv$.
$\FS$ (with or without indices) denotes a filesystem,
and $n$, $m$ and $o$ are nodes in $\setn$.

### 2018-07-07 p2/intro.tex
Single directory value assumption

The approach presented in this paper offers an improvement
over results desribed in \cite{NREC} in multiple ways.
We introduce a new set of commands that is symmetric and
captures more information about the updates.
This has the effect that reasoning about commands
becomes simpler as there are fewer edge cases,
and more powerful as 
predictions made by the reasoning are more accurate
due to the additional information content.
In fact, the new command set not only simplifies
our reconciliation algorithm, but also makes it maximal.
\cite{NREC} also lacked proofs that the update detection
and reconciliation algorithms it presented work as intended,
which we provide in the current paper.
While the results are intuitive, providing rigorous proofs
is far from trivial.
During the process, we define a number of useful concepts
and show their relationships and the properties they possess.
In our view these construct a special algebraic model
that is worthy of interest and of further research on its own.

>>>>

The approach presented in this paper offers an improvement
over results desribed in \cite{NREC} in multiple ways.
We introduce a new set of commands that is symmetric and
captures more information about the updates,
and we restrict information content in directories
to exploit a further hidden symmetry in the command set.
These have the effect that reasoning about commands
becomes simpler as there are fewer edge cases,
and more powerful as 
predictions made by the reasoning are more accurate
due to the additional information content.
In fact, the new command set not only simplifies
our reconciliation algorithm, but also makes it maximal.
\cite{NREC} also lacked proofs that the update detection
and reconciliation algorithms it presented work as intended,
which we provide in the current paper.
While the results are intuitive, providing rigorous proofs
is far from trivial.
During the process, we define a number of useful concepts
and show their relationships and the properties they possess.
In our view these construct a special algebraic model
that is worthy of interest and of further research on its own.
